Quotient Normalized Maximum Likelihood Criterion for Learning Bayesian Network Structures

### 2017-10-03 qnml.tex
typoss

\cite{Suzuki2017} defines regularity for a scoring function $Q_n(X \mid Y)$ as follows:
\begin{definition}
Assume $H_N(X \mid Y') \leq H_N(X \mid Y)$, where $Y' \subset Y.$ We say that $Q_N(\cdot \mid \cdot)$ is regular if $Q_n(X \mid Y') \geq Q_N(X \mid Y)$.
\end{definition}
In the definition, $N$ denotes the sample size, $X$ is some random variable, $Y$ denotes the proposed parent set for $X$, and $H_N(\cdot \mid \cdot)$ refers to the empirical conditional entropy. \cite{Suzuki2017} shows that BDeu violates this principle and demonstrates that this causes the score to prefer more complex networks even though data do not support this. In \cite{Suzuki2017_2}, the authors also suggest that regular scores are computationally more efficient when applied with branch-and-bound type algorithms for Bayesian network structure learning.

>>>>

\cite{Suzuki2017} defines regularity for a scoring function $Q_n(X \mid Y)$ as follows:
\begin{definition}
Assume $H_N(X \mid Y') \leq H_N(X \mid Y)$, where $Y' \subset Y.$ We say that $Q_N(\cdot \mid \cdot)$ is regular if $Q_n(X \mid Y') \geq Q_N(X \mid Y)$.
\end{definition}
In the definition, $N$ denotes the sample size, $X$ is some random variable, $Y$ denotes the proposed parent set for $X$, and $H_N(\cdot \mid \cdot)$ refers to the empirical conditional entropy. \cite{Suzuki2017} shows that BDeu violates this principle and demonstrates that this can cause the score to prefer more complex networks even though data do not support this. In \cite{Suzuki2017_2}, the authors also suggest that regular scores are computationally more efficient when applied with branch-and-bound type algorithms for Bayesian network structure learning.
